---
author: "Fernando Moreno Jabato"
output: 
  html_document:
    df_print: paged
    fig_width: 12
---

<style>
    body .main-container {
        max-width: 90%;
    }
</style>


```{r setup, include=FALSE}
################################################### Load necessary packages
require(knitr)
require(ggplot2)
library(kableExtra)
require(canvasXpress)
require(stringr)

################################################### Load necessary datasets

# Load
metrics <- data[[1]]
  metrics[,1] <- as.character(metrics[,1])  # ID
  metrics[,2] <- as.character(metrics[,2])  # Language
  metrics[,3] <- as.numeric(metrics[,3])  # Size
  metrics[,4] <- as.character(metrics[,4])  # Kernel
  metrics[,5] <- as.character(metrics[,5])  # Feature
  metrics[,6] <- as.character(metrics[,6])  # Value
colnames(metrics) <- c("Exec","Language","Size","Kernel","Feature","Value")


kernel_names <- data[[2]]
  kernel_names[,1] <- as.character(kernel_names[,1]) # Kernel ID
  kernel_names[,2] <- as.character(kernel_names[,2]) # Kernel Name
colnames(kernel_names) <- c("Kernel","Name")

# Take relevant info
languages <- unique(metrics$Language)
sizes <- unique(metrics$Size)
kernels <- unique(metrics$Kernel)
# >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
```





```{r transform_input, echo=FALSE}

# Transform features to languages
invisible(lapply(languages,function(lan){
  metrics$Feature[grepl(paste(lan,"_",sep=""),metrics$Feature)] <<- lan
}))


# Find extra info
indx_memo <- which(grepl("Maximum",metrics$Feature))
indx_time <- which(grepl("Elapsed",metrics$Feature))
indx_cpus <- which(grepl("Percent",metrics$Feature))
# indx_matl <- which(grepl("Matlab",metrics$Feature))

kern_diffs_bySize <- lapply(sizes,function(s){
  kern_diffs <- lapply(kernels,function(k){
    diff <- matrix(NaN,ncol = length(languages)+3, nrow = length(languages))
    colnames(diff) <- c(languages,"Time","CPUs%","Memory")
    rownames(diff) <- languages
    indx_kernel <- which(metrics$Kernel == k & metrics$Size == s)
    invisible(lapply(languages,function(x){
      indx_x <- intersect(which(metrics$Language == x),indx_kernel)
      invisible(lapply(languages,function(y){
        indx_y <- which(metrics$Feature == y)
        if(length(intersect(indx_x,indx_y))>0){
          diff[x,y] <<- metrics$Value[intersect(indx_y,indx_x)[1]]
          diff[y,x] <<- metrics$Value[intersect(indx_y,indx_x)[1]]        
        }
      }))
      # Add time
      aux = intersect(indx_x,indx_time)
      if(length(aux)>0){
        diff[x,"Time"] <<- metrics$Value[aux[1]]      
      }
      # Add CPU
      aux = intersect(indx_x,indx_cpus)
      if(length(aux)>0){
        diff[x,"CPUs%"] <<- metrics$Value[aux[1]]     
      }
      # Add memory
      aux = intersect(indx_x,indx_memo)
      if(length(aux)>0){
        diff[x,"Memory"] <<- metrics$Value[aux[1]]      
      }
    })) 
    return(diff)
  })
  names(kern_diffs) <- kernels
  return(kern_diffs)
})

# Add sizes info
names(kern_diffs_bySize) <- sizes

# Print in console
# kern_diffs_bySize


# >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
```


```{r exp_texts,echo=FALSE}
# Sizes 
out_siz <- unlist(lapply(sizes,function(names){paste("* ",names,sep="")}))
# Languages
out_lan <- unlist(lapply(languages,function(names){paste("* ",names,sep="")}))
# Kernels
out_ker <- unlist(lapply(seq(nrow(kernel_names)),function(i){paste("* (",kernel_names$Kernel[i],") ",kernel_names$Name[i],sep="")}))
```



# **Kernels benchmark esperiment**

## **Used data**
This resport contains results about different experiments using different kernel implementations over a double square symetric matrix of different sizes. In this case, **sizes** have been:

`r paste(knit(text = paste(out_siz,collapse = "\n")),collapse = "\n")`

These matrices have been kernelized using (`r length(kernels)`) different **kernel algorythms**:

`r paste(knit(text = paste(out_ker,collapse = "\n")),collapse = "\n")`

And all these kernels have been implemented using (`r length(languages)`) **programming languages**:

`r paste(knit(text = paste(out_lan,collapse = "\n")),collapse = "\n")`


## **Results**
```{r show_results, echo = FALSE}
# kable(metrics)
metrics
```


```{r prepare_canvas, echo = FALSE}
require(plyr)
y <- as.data.frame(do.call(rbind,lapply(seq_along(kern_diffs_bySize),function(j){
  curr_size <- names(kern_diffs_bySize)[j]
  kern_values <- as.data.frame(do.call(cbind,lapply(seq_along(kern_diffs_bySize[[j]]),function(i){
    #Load
    kern_diffs <- kern_diffs_bySize[[j]]
    kernel_name <- names(kern_diffs)[i]
    values <- kern_diffs[[i]]
    # Transform
    values <- t(values)
    colnames(values) <- paste(colnames(values),kernel_name,sep="_")
    # Special cases
    if("CPUs%" %in% rownames(values)){
      values["CPUs%",] <- gsub("%","",values["CPUs%",])
    }
    if("Time" %in% rownames(values)){
      values["Time",] <- unlist(lapply(values["Time",],function(time){
        if(str_count(time,":") == 1){
          return(paste("0:",time,sep=""))
        }
        return(time)
      }))
      # Transform time variable
      values["Time",] <- unlist(lapply(values["Time",],function(time){
        hms <- unlist(strsplit(time,":"))
        seconds <- as.numeric(hms[1])*3600 + as.numeric(hms[2])*60 + as.numeric(hms[3])
      }))  
    }
     
    # Prepare rownames
    values <- as.data.frame(values,stringsAsFactors = F)
    rownames(values) <- paste(rownames(values),curr_size,sep="_")
    # Return
    return(values)
  })))
  return(kern_values)
})))
y <- y[order(nchar(rownames(y)),rownames(y)),order(nchar(colnames(y)),colnames(y))]
# # X: samples (y.col) parameters
x <- data.frame(Kernel = unlist(lapply(colnames(y),function(coln){tail(unlist(strsplit(coln,"_")),1)})),
                Language = unlist(lapply(colnames(y),function(coln){head(unlist(strsplit(coln,"_")),1)})))
rownames(x) <- colnames(y)

# Z : variables (y.row) parameters
z <- data.frame(Language = unlist(lapply(rownames(y),function(coln){head(unlist(strsplit(coln,"_")),1)})),
                Size = unlist(lapply(rownames(y),function(coln){tail(unlist(strsplit(coln,"_")),2)[1]})),
                stringsAsFactors = FALSE)
rownames(z) <- rownames(y)


################################### ONLY FOR PAPER PLOTS
# aux_names <- data.frame(From = c("Matlab","Ruby","Python"), 
#                         To = c("Mat","Rub","Pyt"),
#                         stringsAsFactors = FALSE)

# # Substitute 
# invisible(lapply(seq(nrow(aux_names)),function(i){
#   rownames(x) <<- gsub(aux_names$From[i],aux_names$To[i],rownames(x))
#   colnames(y) <<- gsub(aux_names$From[i],aux_names$To[i],colnames(y))
# }))

###################################

message("X:")
x
message("Y:")
y
message("Z:")
z

```

```{r plot_canvas, echo = FALSE, eval = TRUE}
aux <- y
tmp_zeros_i <- c()
tmp_zeros_j <- c()
invisible(lapply(seq(nrow(y)),function(i){
  invisible(lapply(seq(ncol(y)),function(j){
    if(!is.nan(y[i,j])){
      if(y[i,j] == 0){
        tmp_zeros_i <<- c(tmp_zeros_i,i)
        tmp_zeros_j <<- c(tmp_zeros_j,j)  
      }else{
        aux[i,j] <<- -log10(as.numeric(y[i,j]))
      }
    }
  }))
}))

################################################################## REMOVE THIS FOR FINAL VERSION

# 
variables_to_remove <- which(!z$Language %in% languages)
#samples_to_remove <- which(x$Kernel %in% c("rf","vn0.1"))


# Add also (as special cases, Matlab vs Matlab)
# invisible(lapply(which(x$Language == "Matlab"),function(j){
#   invisible(lapply(which(z$Language == "Matlab"),function(i){
#     # Find maximum of it kernel
#     max_kern <- max(as.numeric(unlist(aux[-variables_to_remove,which(x$Kernel == x$Kernel[j])])),na.rm=TRUE)
#     aux[i,j] <<- max_kern
#   }))
# }))
################################################################## REMOVE THIS FOR FINAL VERSION

# Update zeros
if(length(tmp_zeros_i)>0){
  invisible(lapply(seq_along(tmp_zeros_i),function(k){
    if(length(variables_to_remove) > 0){
      max_kern <- max(as.numeric(unlist(aux[-variables_to_remove,which(x$Kernel == x$Kernel[tmp_zeros_j[k]])])),na.rm=TRUE)
    }else{
      max_kern <- max(as.numeric(unlist(aux[,which(x$Kernel == x$Kernel[tmp_zeros_j[k]])])),na.rm=TRUE)      
    }
    aux[tmp_zeros_i[k],tmp_zeros_j[k]] <<- max_kern
  }))
}




###################### Plot circos
circos_by_languages <- function(y,x,z, target_var_languages, title, ring_weight = 150){
  canvasXpress(
    data=y[which(z$Language %in% target_var_languages),],
    smpAnnot=x,
    varAnnot=z[which(z$Language %in% target_var_languages),],
    graphType="Circular",
    ringGraphType=as.list(rep("heatmap",nrow(x))),
    ringGraphWeight=as.list(rep(ring_weight,nrow(x))),
    segregateSamplesBy=list("Kernel"),
    segregateVariablesBy=list("Language"),
    smpOverlays=list("Kernel"),
    # smpLabelRotate = 45,
    title=title,
  )
}
circos_by_languages(aux,x,z,languages,"Error (-log10) benchmark",ring_weight = 300)
circos_by_languages(y,x,z,languages,"Error benchmark")
circos_by_languages(y,x,z,c("Time"),"Times (s) benchmark")
circos_by_languages(y,x,z,c("CPUs%"),"CPUs (%) benchmark")
circos_by_languages(y,x,z,c("Memory"),"Memory (kb) benchmark")

```
